\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-12 ext-ind-type-compilation-example.tex
FIxing Diagram
Save. Fixing

\definecolor{codecomment-color}{HTML}{FF007F}

\begin{lstlisting}
Family STLC.[@\tanc{Ext-Ind-Cmp-start}@]
 FInductive tm : Set := tm_var : [@\dadada@]
 (* [@\dadada@] other constructors *) 
 FScheme tm_prec PRecT about self__STLC.tm.
 FScheme Comp about self__STLC.tm_prec.
 (* Generate Partial Recursor 
    and the computational axiom for tm *)
 FRecursion subst on tm 
 motive (fun _ => id → tm → tm). 
  Case tm_var := fun s x t => 
    if (eqb x s) then t else (tm_var s).
  (* [@\dadada@] other cases *)
 End subst.
(* Field test := (subst (tm_var 0) 0 (tm_var 0)). *)
(* [@\dadada@] other things in STLC *)
EndFamily.
Family STLC_bool extends STLC.
 Extend FInductive tm : Set :=
  | tm_true : tm [@\dadada@]
  (* [@\dadada@] other new constructors *)
 FRecursion subst.
  Case tm_true := fun x t => tm_true.
  (* [@\dadada@] other extended cases *)
 End subst. 
 Inherits subst.
(* [@\dadada@] other things in STLC_Bool *)
EndFamily.
[@\tanc{Ext-Ind-Cmp-end}@]
\end{lstlisting}

\makeline[0pt]{Ext-Ind-Cmp-start}{Ext-Ind-Cmp-end}[codecomment-color!50]
% \vspace{-3pt}

@@

\begin{lstlisting}
(* Compilation Of the above *) [@\tanc{Cmp-Result0-start}@]
Module Type STLC_Interface. 
  Parameter (tm : Set).
  Parameter (tm_var : id → tm).
  Parameter (tm_abs : id → tm → tm).
  (* [@\dadada@] and all the fields for inductive type [@\dadada@] *)
End STLC_Interface.
(* Collect eliminator to Set for tm *)
Module tm_rec_type (STLC: STLC_Interface).
  Definition __recursor_type_tm_rec :=
    forall P : STLC.tm -> Set,
    (forall n : id, P (STLC.tm_var n)) ->
    (forall (n : id) (i : STLC.tm),
    P i -> P (STLC.tm_abs n i)) ->
    [@\dadada@] -> forall i : STLC.tm, P i.
End tm_rec_type.  
Module tm_prec_72 (self__STLC: STLC_Interface).
Definition tm_prec :
  forall i : tm, forall P : tm -> Type,
  (forall n, option (P (tm_var n))) ->
  [@\dadada@], option (P __i) :=
End tm_prec_72. 
Module Type substtm_139 (self__STLC: [@\dadada@]).
Parameter
  (subst_on_tm_unit :
	 eq (self__STLC.subst (self__STLC.tm_unit))
       self__STLC.subst_internal.tm_unit).
(* [@\dadada@] subst equality on other constructors *)
End substtm_139. 
[@\tanc{Cmp-Result0-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
(* Compiled Field STLC.subst_internal.tm_var *) [@\tanc{Cmp-Result-start}@]
Module tm_var_handle (self__STLC: STLC_Interface)
    (self__subst_internal: EmptySig_84).
  Definition tm_var :
    forall (s : ident) (x : ident) 
    (t : self__STLC.tm), self__STLC.tm :=
    fun s x t => if eqb x s
       then t else self__STLC.tm_var s.
End tm_var_handle. (* [@\dadada@] and more *)
(* Assembling STLC.subst_internal when compilation *)
Module subst_internal_410 (STLC: STLC_Interface). 
 Module subst_internal.
 Include tm_var_handle STLC. Include tm_abs_handle STLC.
 Include tm_app_handle STLC. Include tm_unit_handle STLC.
 End subst_internal.
End subst_internal_410.
(* Intermediate Module solely for type checking *)
Module do_tc (STLC: STLC_Interface).
  Include tm_rec_type STLC.
  Parameter (recursor_for_type_checking 
    : __recursor_type_tm_rec).
  Definition term_for_type_checking :=
    recursor_for_type_checking 
      (fun _  ⇒ id → STLC.tm → STLC.tm)
      subst_internal_410.tm_var [@\dadada@] .
End do_tc.
(* Ctx that expose concrete inductive type *)
Module Type ctx_subst_113.
Inductive __internal_tm : Set := [@\dadada@] 
Include subst_internal_410. (* [@\dadada@] and more inclusion *)
End ctx_subst_113.
(* Compilation of recursor, not reusable
    when inductive type extended due to the ctx *)
Module subst_128 (self__STLC: ctx_subst_113).
Include __motive_of_subst_107 self__STLC.
Definition subst :=
  self__STLC.__internal_tm_rec __motiveTsubst
	self__STLC.subst_internal.tm_var [@\dadada@] .
End subst_128.
(* Assembling the whole STLC *)
Module STLC.
Include tm_5. Include tm_prec_72. Include tm_prectm_81.
Include subst_internal_410. Include subst_128.
End v_129.
(* Assembling STLC_bool.subst_internal via reusing 
    most of the former compilation results *)
Module subst_internal_248 (STLC_bool: STLC_Interface).
Include tm_true_197 STLC_bool. Include [@\dadada@]
(* The Reused Compilation result *)
Include tm_var_handle STLC_bool. Include [@\dadada@]
End v_248. 
(* Regenerated FRecursion result *)
Module subst_242 (self__STLC_bool: [@\dadada@]).
Include __motive_of_subst_107 self__STLC_bool.
Definition subst :=
  self__STLC_bool.__internal_tm_rec __motiveTsubst
	self__STLC_bool.subst_internal.tm_var [@\dadada@]
    self__STLC_bool.subst_internal.tm_true [@\dadada@] .
End subst_242. [@\tanc{Cmp-Result-end}@]
\end{lstlisting}

>>>>

@@

\begin{lstlisting}
(* **Type Checking of Inductive Type** *) [@\tanc{Cmp-Result0-start}@]
Module Type STLC_Ctx1. 
(* The Context including Inductive Type *)
  Parameter (tm : Set).
  Parameter (tm_var : id → tm).
  Parameter (tm_abs : id → tm → tm).
  (* [@\dadada@] and all the fields for inductive type [@\dadada@] *)
End STLC_Ctx1.
Module Type tm_prec_64 (self: tm_6). (* Type for partial recursor *)
Parameter
  (tm_prec :
  forall i : self.tm, forall P : self.tm -> Type,
  (forall n, option (P (self.tm_var n))) ->
  [@\dadada@], option (P i)).
End tm_prec_64.
Module Type STLC_Ctx2. (* The Context including partial recursor *) 
  Include STLC_Ctx1.
  Include tm_prec_64.
End STLC_Ctx2.
(* [@\dadada@] etc, for every context, (everytime a new field is added) we will construct a new context as module type *)
(* Collect eliminator TYPE for later type-check *)
Module tm_rec_type (self: STLC_Ctx1).
  Definition __recursor_type_tm_rec :=
    forall P : self.tm -> Set,
    (forall n : id, P (self.tm_var n)) ->
    (forall (n : id) (i : self.tm),
    P i -> P (self.tm_abs n i)) ->
    [@\dadada@] -> forall i : self.tm, P i.
End tm_rec_type.  
(* **Type checking of Recursion** *)
(* Typecheck each handler, here STLC.subst.tm_var *)
(* Also an example of fields in nested family, thus with two contexts *) 
Module tm_var_handle (self__STLC: STLC_Ctx1)
    (self__subst_internal: EmptySig_84).
  Definition tm_var :
    forall (s : ident) (x : ident) 
    (t : self__STLC.tm), self__STLC.tm :=
    fun s x t => if eqb x s
       then t else self__STLC.tm_var s.
End tm_var_handle. (* [@\dadada@] and more *)
(* Assembling tycked handlers in STLC.subst during compilation *)
Module subst_internal_410 (STLC: STLC_Ctx1). 
 Module subst_internal.
 Include tm_var_handle STLC. Include tm_abs_handle STLC.
 Include tm_app_handle STLC. Include tm_unit_handle STLC.
 End subst_internal.
End subst_internal_410.
(* Intermediate Module solely for exhausitivity checking *) 
Module do_tc (self: STLC_Ctx[@\dadada@]).
  Include tm_rec_type self.
  Parameter (recursor_for_type_checking 
    : __recursor_type_tm_rec).
  Definition term_for_type_checking :=
    recursor_for_type_checking 
      (fun _  ⇒ id → self.tm → self.tm)
      subst_internal_410.tm_var [@\dadada@] .
End do_tc.
[@\tanc{Cmp-Result0-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
[@\tanc{Cmp-Result-start}@]
(* Exposing Computational Axiom into Ctx *)
Module Type substtm_139 (self: STLC_Ctx[@\dadada@]).
Parameter
  (subst_on_tm_unit :
	 (self.subst (self.tm_unit)) = 
      self.subst_internal.tm_unit).
(* [@\dadada@] subst equality on other constructors *)
End substtm_139.

(* Compilation, only when closing a top-level family *)
(* Ctx that expose concrete inductive type *)
Module Type ctx_subst_113.
Inductive __internal_tm : Set := [@\dadada@] 
Include subst_internal_410. (* [@\dadada@] and more inclusion *)
End ctx_subst_113.
(* Compilation of recursor, 
  require concrete inductive type in the ctx *)
Module subst_128 (self: ctx_subst_113).
Include __motive_of_subst_107 self.
Definition subst :=
  self.__internal_tm_rec __motiveTsubst
	self.subst_internal.tm_var [@\dadada@] .
End subst_128.
(* Compilation of Partial Recursor *)
Module tm_prec_72 (self: STLC_Ctx1).
Definition tm_prec :
  forall i : self.tm, forall P : self.tm -> Type,
  (forall n, option (P (self.tm_var n))) ->
  [@\dadada@], option (P i) :=
End tm_prec_72. 
(* Assembling/Compiling the whole STLC *)
Module STLC.
Include tm_5. Include tm_prec_72. Include tm_prectm_81.
Include subst_internal_410. Include subst_128.
End v_129.
(* Assembling STLC_bool.subst_internal via reusing 
    most of the former compilation results *)
Module subst_internal_248 (STLC_bool: STLC_Ctx1).
Include tm_true_197 STLC_bool. Include [@\dadada@]
(* The Reused Compilation result *)
Include tm_var_handle STLC_bool. Include [@\dadada@]
End v_248. 
(* Regenerated FRecursion result *)
Module subst_242 (self__STLC_bool: [@\dadada@]).
Include __motive_of_subst_107 self__STLC_bool.
Definition subst :=
  self__STLC_bool.__internal_tm_rec __motiveTsubst
	self__STLC_bool.subst_internal.tm_var [@\dadada@]
    self__STLC_bool.subst_internal.tm_true [@\dadada@] .
End subst_242. [@\tanc{Cmp-Result-end}@]
\end{lstlisting}
